The Heavy Photon Search Test Detector

### 2013-11-19 hps-testrun-nim.tex
Updating SVT hit efficiency plot.

While occupancy was slightly larger than expected, good agreement between data and simulation was 
found after taking into account dead or noisy channels. The hit efficiency was estimated by measuring 
the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close to 
in the edge region are excluded in the calculation of the single hit efficiency. The hit efficiency, see 
Fig.~\ref{fig:hit_efficiency}, was measured to be above 98\% and fairly uniform across the SVT.
\begin{figure}[h]
\begin{center}
{\small
    	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
        \caption{ The hit reconstruction efficiency as a function of detector layer.}
	\label{fig:hit_efficiency}
}
\end{center}
\end{figure}
The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
The single-hit resolution for charged particles with signal to noise ration above 20, as demonstrated here, 
is relatively constant at approximately 6~$\mu$m for tracks that are close to normal to the sensors as in HPS.

>>>>

While occupancy was slightly larger than expected, good agreement between data and simulation was 
found after taking into account dead or noisy channels. The hit efficiency was estimated by measuring 
the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close to 
in the edge region are excluded in the calculation of the single hit efficiency. The hit efficiency, see 
Fig.~\ref{fig:hit_efficiency}, was measured to be above 98\% and fairly uniform across the SVT.
\begin{figure}[h]
\begin{center}
{\small
    	\includegraphics[width=7cmh]{figures/single_hit_efficiency_Omar_11192013.pdf}
        \caption{ The hit reconstruction efficiency as a function of detector layer.}
	\label{fig:hit_efficiency}
}
\end{center}
\end{figure}
The spatial resolution of similar microstrip sensors is well established by test beam data, against which 
the charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
The single-hit resolution for charged particles with signal to noise ratio above 20, as demonstrated 
here, is relatively constant at approximately 6~$\mu$m for tracks that enters approximately normal to the 
sensors as in HPS.
